---
title: "Creating Vectors"
author: 
    name: "Monique Hernandez"
    affiliation: University of California, Santa Barbara
date: "Augustt 18, 2026"
format:
  html:
    toc: true
execute:
  message: false
  warning: false
---
[click here for github link](https://github.com/moniqueallyson/eds221day2) 


# Creating vectors

# Integers
```{r}
integer(5)
```

# Sequence operator
```{r}
1:5
```

# seq() function

```{r}
seq(1, 5)
seq(2004, 2024, by = 2)
```
# c() "combine"

```{r}
c(1L, 2L, -1L)
```

# Sampling random numbers from a distribution
```{r}
rpois(5, lambda = 10)
```
# Doubles (i.e., decimals)

# double ()
```{r}
double(5)

# c()
c(1, 2, -1)

# seq() function
seq(1, 5, by = 0.9)
seq(1, 5, length.out = 4)
```


# Random numbers
```{r}
rnorm(5, mean = 5, sd = 2)
```

# Others
```{r}
# Coercion
1L / 2L

# Characters

# Character
character(5)

# c()
c("R", "Python", "SQL")
```
# What happens if we drop the quotes?

::: {.callout-important}
What happens if you type this: c(R, Python, SQL), without the quotes?

R will interpret them as variables and may not find the object "R".
:::

```{r}
# What is the type of this vector?
c("1", "2", "3")

# Logical

# logical()
logical(5)

# c()
c(TRUE, FALSE)
#This is useless
```

# Relational operators
```{r}
5 > 1
5 > 3:6
"R" == "Python"
```

# Predicates (any function that returns logic)
```{r}
3:6 > 2
all(3:6 > 2)

5:10 > 7
any(5:10 > 7)
```
